Workflow and Software Documentation

### 2013-07-08 Workflow.Rnw
added plotting example

@@

A reasonable workflow is this:
\begin{enumerate}
\item 
<<message=FALSE>>=
source("Econ-Growth-Resampling.R")
@
\item
Execute the function called \function{genAllResampleData()} in this file 
from the Console. A typical call would be 
<<eval=FALSE>>=
genAllResampleData(method="wild", n=100)
@
\item Reload the data using one of the various "load" functions
from file \texttt{Econ-Growth-Functions2.R}:

@@

\begin{enumerate}
\item
A typical call for loadAllResampleData would be
<<eval=FALSE>>=
loadAllResampleData(modelType="cde", energyType="Q")
@
\item
Another example:
<<>>=
head(loadAllResampleData(model="sf", factor="K"), n=5)
@
\end{enumerate}
\end{enumerate}
\end{document}

>>>>

<<setup, include=FALSE>>=
require(knitr)
opts_chunk$set(
  tidy=FALSE
)
@

@@

A reasonable workflow is this:
\begin{enumerate}
\item 
<<message=FALSE>>=
source("Econ-Growth-Resampling.R")
@
\item
Execute the function called \function{genAllResampleData()}.

A typical call would be 
<<eval=FALSE>>=
genAllResampleData(method="wild", n=100)
@
\item Reload the data using one of the various "load" functions
from file \texttt{Econ-Growth-Functions2.R}:

@@

\begin{enumerate}
\item
A typical call for loadAllResampleData would be
<<eval=FALSE>>=
loadAllResampleData(modelType="cde", energyType="Q")
@
\item
Another example:
<<>>=
head(loadAllResampleData(model="sf", factor="K"), n=5)
@
\end{enumerate}
\item
Plots of resampling distributions can be made with \function{triPlot()}.
<<>>=
source("Graphics.R")
resData <- loadAllResampleData(modelType="cde", energyType="Q")
triPlot( subset(resData, method=="wild"), 
         gamma, alpha, beta,
         labels=c("gamma", "alpha", "beta"),
         n.grid=5,  aes_string="color=lambda", 
         size=3, alpha=.5 ) + 
     geom_point( data=subset(resData, method=="orig"), 
                 color="red", alpha=1, size=3) +
     facet_wrap( ~ countryAbbrev )
@
Eventually, we can build a wrapper that loads the data and builds the plot with our favorite settings.
\end{enumerate}
\end{document}
